Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-04 article.tex
bookmark

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}.

@@

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Recoveries of scenes shown in
    \cref{fig:distributions}. Color represents aerosol density, in
    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    images simulated by single-scattering are used as input for the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze      & Forward        & Aerosol          & Isotropic       & Absorbing & $\epsilon~~$ & $\delta_{\rm mass}$ \\
    scene     & model          & density [$1/{\rm m}^3$]    & phase function? & aerosol?  &            &  \\
     \midrule
    Front       & Single scatter & ${\mathcal{O}}(10^{6})$         &                 &           & 18\%       & 1.1\%  \\
               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 &           & 65\%       & 14\%  \\
    \cmidrule(r){1-5}
     Blobs       & Single scatter & ${\mathcal{O}}(10^{6})$         &                 &           & 14\%       & 0\%  \\
               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 &           & 65\%       & 6.7\%  \\
               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         & $\surd$         &           & 49\%       & 2\%  \\
               & Monte Carlo    & ${\mathcal{O}}(10^{6})$         &                 & $\surd$   & 83\%       & 9.6\%  \\
               & Monte Carlo    & ${\mathcal{O}}(10^{7})$         &                 &           & 98\%       & 23\%  \\
    \bottomrule
  \end{tabular}
  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\

>>>>

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}. \hl{Figs. 6.3 to Fig. 6.14 in every comparison, for display purposes both images underwent same contrast streching operations, and used the same colormap}.

@@

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Recoveries of scenes shown in
    \cref{fig:distributions}. Color represents aerosol density, in
    units of $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    images simulated by single-scattering are used as input for the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
     \midrule                                                                                             
    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 1.1\%               & 18\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -14\%               & 65\%         \\
    \cmidrule(r){1-5}                                                                                     
     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 6.7\%               & 65\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & -2\%                & 49\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & 9.6\%               & 83\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & 23\%                & 98\%         \\
    \bottomrule
  \end{tabular}
  \caption{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\
